Combining genomic prediction with citizen science for crop improvement, as case study with “early selection” in durum wheat

### 2019-05-27 manuscript/outline.Rmd
add_data
25052018

---
output: 
  word_document:
    reference_docx: "common/word-styles-reference-01.docx"
---

@@

# Combining genomic prediction with citizen science for crop improvement, as case study with “early selection” in durum wheat

>>>>

---
title: "Combining genomic prediction with citizen science for crop improvement, as case study with “early selection” in durum wheat"
output: 
  word_document:
    reference_docx: "library/word-styles-reference-01.docx"
---

@@
